Are We Reusing Outdated and Licensed Code from Stack Overflow?

### 2017-02-14 cloneoverflow-latex/cloneoverflow.tex

Kapser et al.~studied clones in Linux file systems and create 11 patterns of code cloning based on four groups: Forking, Templating, Customization and Exact match~\cite{Kapser2003,Kapser2008}. Our study adopted one of the patterns into our online code cloning patterns.

>>>>

Kapser et al.~studied clones in Linux file systems and create 11 patterns of code cloning based on four groups: Forking, Templating, Customisation and Exact match~\cite{Kapser2003,Kapser2008}. Our study adopted on of the patterns into our online code cloning patterns.
